%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Technical Account Manager Intern} % Job title
    {Tanium} % Organization
    {Emeryville, CA} % Location
    {June 2019 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Played significant role in creating an autograder to test the progress of new hires in learning the Tanium platform. Collaborated with project manager and several other engineers to remediate this business problem.}
        \item {Attended weekly customer cadence calls and helped solve day-to-day issues that customers confronted.}
        \item {Completed quality assurance tests on a routine basis to ensure the correctness of the software.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Edwards Lifesciences} % Organization
    {Irvine, CA} % Location
    {June 2018 - August 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Facilitated progression of various projects using Jira Software to delegate tasks and bug fixes to team.}
        \item {Wrote application to automate documentation for various manufactured hardware parts.}
        \item {Ran comprehensive tests on builds for several new software releases, included tests of hardware under extreme conditions and use of high risk equipment in lab.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Marketing} % Job title
    {RockWithThis} % Organization
    {Oakland, CA} % Location
    {September 2018 - March 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Started internship program for small startup and garnered a role in marketing strategy with founders.}
        \item {Spread awareness of company on the Berkeley campus via control of social media.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
